Template for indicator documentation

### 2022-08-03 02-structure.Rmd
Faktaark

## Test 1 {-}
This indicator is about ....

## Test 2 {-}
And this indicator is about...

>>>>

## Areal av isbreer / Glacier area {-}
This indicator is about ....

```{r, echo=F}
source("indicators/indicatorMetaData/Areal av isbreer.R")
knitr::kable(t(out), 
            format = "html",
            caption = paste("Fakatark for tilstandindikatoren ", 
                        out$Indikator, col.names = NULL))
```

## Indicator X {-}
And this indicator is about...

### 2022-08-03 indicators/workingFiles/template.Rmd
Faktaark

---
title: "Template for indicator documentation"
output:
  pdf_document
---

<!-- This is a template for how to document the indicator analyses. 
Make a copy of this file and sore it in the same folder (indicators/workingFiles/) 
before starting. This is a working file. It is also a stand-alone Rmd file
inside a bookdown project. Therefore, to knit the file for preview reasons,
you need to type rmarkdown::render("indicators/workingFiles/template.Rmd") 
in the console, as the the usual Ctrl + Alt + k will not work. When the analyses is complete,
Anders Kolstad or someone else will perform a rapid code review, making sure 
the analyses is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. When completed, Anders will make a copy
of the working file and put it in the folder below (indicators/). After modifying it
slightly (mainly removing the top YAML header) the output will become available 
on the website (https://ninanor.github.io/ecosystemCondition/) -->

@@

>>>>

---
title: "Template for indicator documentation"
output:
  html_document
---

<!-- This is a template for how to document the indicator analyses. 
Make a copy of this file and sore it in the same folder (indicators/workingFiles/) 
before starting. This is a working file. It is also a stand-alone Rmd file
inside a bookdown project. Therefore, to knit the file for preview reasons,
you need to type rmarkdown::render("indicators/workingFiles/template.Rmd") 
in the console, as the the usual Ctrl + Alt + k will not work. When the analyses is complete,
Anders Kolstad or someone else will perform a rapid code review, making sure 
the analyses is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. When completed, Anders will make a copy
of the working file and put it in the folder below (indicators/). After modifying it
slightly (mainly removing the top YAML header) the output will become available 
on the website (https://ninanor.github.io/ecosystemCondition/). -->

@@

add more detailed instruction about georeferencing ect
...
